Reasoning About a Machine with Local Capabilities

### 2018-04-28 toplas/paper.tex
Added cofe definitions to appendix

>>>>

\subsection{Complete ordered family of equivalences (c.o.f.e)}
\label{app:cofe}
This is an excerpt from \citet{Birkedal:tutorial-notes} about c.o.f.e.'s.
\begin{definition}[o.f.e.] An \emph{ordered family of equivalence} (o.f.e) is a
  set and a family of equivalences $\left(X, \left( \nequal \right)_{n=0}^\infty
  \right)$ that satisfy the following properties: 
  \begin{itemize}
  \item $\nequal[0]$ is the total relation on $X$
  \item $\forall n \ldotp \forall x,y \in X \ldotp x \nequal[n+1] y \Rightarrow
    x \nequal y$
  \item $\forall x,y \in X \ldotp (\forall n\ldotp x \nequal y) \Rightarrow x = y$
  \end{itemize}
\end{definition}

\begin{definition}[c.o.f.e.] A \emph{complete} ordered family of equivalences
  (c.o.f.e) is an o.f.e $\left(X, \left( \nequal \right)_{n=0}^\infty \right)$
  where all Cauchy sequences have a limit.  
\end{definition}
